---
title: "Project 2 Isabella Morse"
output: html_notebook
---
#Introduction

Scientific Question:
Are the sequences and structure of the EpCAM protein in metastatic breast cancer in humans similar to other species with metastatic breast cancer?

...Need protein background...


Scientific Hypothesis:
If the EpCAM gene is overexpressed in metastatic breast cancer in humans, then it's protein sequence and structure will be similar to other species that also have metastatic breast cancer.   

...description of analyses and how data was downloaded..

Package Descriptions

...define these in your own words - at least 3 packages needed to be used and at least 5 sentences per package with links to resources to the packages need to be included...
 
#Performing Bioinformatics Analyses
 Loading in the data from Uniprot download
```{r}

```
 
#Homology Models
```{r}
plot(cars)
```

#Upload Pymol model
```{r}

```

#Multiple sequence alignment 
```{r}

```

#Plotting (phylogenetic clustering)
```{r}

```

Analysis of Results 
....
